Streaking and Clutching in Round-Based First Person Shooter Esports

### 2022-07-17 presentation.qmd
add spacing to last slide
more formatting

::: fragment
-   Round win % after a streak of 3 round wins:
-   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
-   Actual: **`r 100 * round(round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r round_win_prop_after_b2b2b_wins$n` / `r round_win_prop_after_b2b2b_wins$total` )
:::

@@

@@

::: {.column width="30%"}
| Plant side |                           \% |
|------------|-----------------------------:|
| Primary    | `r plant_site_prop[['pri']]` |
| Secondary  | `r plant_site_prop[['sec']]` |
:::

@@

::: {.column width="30%"}
| Plant side |                            Win % |
|------------|---------------------------------:|
| Primary    | `r plant_site_win_prop[['pri']]` |
| Secondary  |     `r plant_site_prop[['sec']]` |
:::

>>>>

<br/><br/>

::: fragment
-   Round win % after a streak of 3 round wins:
    -   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
    -   Actual: **`r 100 * round(round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r round_win_prop_after_b2b2b_wins$n` / `r round_win_prop_after_b2b2b_wins$total`)
:::

@@

<br/><br/>

@@

::: {.column .fragment width="30%"}
| Plant site |                           \% |
|------------|-----------------------------:|
| Primary    | `r plant_site_prop[['pri']]` |
| Secondary  | `r plant_site_prop[['sec']]` |
:::

@@

::: {.column .fragment width="30%"}
| Plant site |                            Win % |
|------------|---------------------------------:|
| Primary    | `r plant_site_win_prop[['pri']]` |
| Secondary  | `r plant_site_win_prop[['sec']]` |
:::
